### 2025-02-10 skripsi/acknowledgments.tex
update title to using instead of with, add more to acknowledgements

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection{}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\begin{center}
 \textbf{\large ACKNOWLEDGMENTS}\\[3em]
\end{center}
%-----------------------------------------
\noindent I would like to take the time to acknowledge my friends, family, and everyone who have taken the time to support and encourage me through the completion process of my degree.
% \noindent Kata pengantar berperan sebagai gerbang masuk bagi pembaca dan mendapat sajian ringkas tentang hal-hal terkait paparan pada buku Tugas Akhir (TA). Sajian ini sejatinya merupakan pengenalan umum bagi pembaca tentang isi tulisan. Hal ini berbeda dengan abstrak yang mendeskripsikan pekerjaan dan hasil penelitian secara lebih teknis.

>>>>

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection{}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\begin{center}
 \textbf{\large ACKNOWLEDGMENTS}\\[3em]
\end{center}
%-----------------------------------------
\noindent I would like to take the time to acknowledge my friends, family, and everyone who have taken the time to support and encourage me through the completion process of my degree. Through this work, I hope to be able to contribute to our understanding of the world. I also would like to thank all the professors and academic staff who have helped me to achieve this goal. At some points, parts of this work seemed endless and insurmountable. However, the support everyone has given me has been instrumental in surpassing those obstacles.

On a more academic note, this work takes our knowledge of how the spectral method works and uses that as a basis for cases for when the systems are too complex, or not fully modeled mathematically. This means that, akin to how one would manually derive the solution coefficients from parameter coefficients in the spectral method, the proposed SpectralSVR would model the  relationship between solution coefficients and parameter coefficients from data. Building on previous work, our contribution also include interpretation of the learned relationship between coefficients. The proposed method exposes the learned relationship as the contributions of each parameter coefficient towards each solution coefficient. More specifically, I would like to acknowledge the works of \textcite{fanaskovSpectralNeuralOperators2023,du2024neural,ustunVisualisationInterpretationSupport2007} which have been the inspiration for the proposed approach.

% \noindent Kata pengantar berperan sebagai gerbang masuk bagi pembaca dan mendapat sajian ringkas tentang hal-hal terkait paparan pada buku Tugas Akhir (TA). Sajian ini sejatinya merupakan pengenalan umum bagi pembaca tentang isi tulisan. Hal ini berbeda dengan abstrak yang mendeskripsikan pekerjaan dan hasil penelitian secara lebih teknis.

### 2025-02-10 skripsi/identitas.tex
update title to using instead of with, add more to acknowledgements

%JUDUL: 
\providecommand{\judul}{approximating solutions of governing equations with Fourier transform and support vector machine}
\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations With Fourier Transform and Support Vector Machine}
%PENULIS:
\providecommand{\penulis}{Ahmad Izzuddin}
%NIM:
\providecommand{\nim}{1908919}

>>>>

%JUDUL: 
\providecommand{\judul}{approximating solutions of governing equations using Fourier transform and support vector machine}
\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations Using Fourier Transform and Support Vector Machine}
%PENULIS:
\providecommand{\penulis}{Ahmad Izzuddin}
%NIM:
\providecommand{\nim}{1908919}
